---
title: "COVID-19 Data: "
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    social: menu
    source: embed
---

```{r}
library(flexdashboard)
library(tidyverse)
library(socviz)
library(covid19R)
library(covdata)
library(coronavirus)
## Global options ----
# chunk options ----
knitr::opts_chunk$set(
  echo = FALSE,
  cache = FALSE,
  prompt = FALSE,
  tidy = FALSE,
  comment = "#> ",
  message = FALSE,
  warning = FALSE, 
  fig.path = "figs/")
ggplot2::theme_set(ggthemes::theme_economist_white(base_size = 10, 
                                                   gray_bg = FALSE, 
                                                   horizontal = FALSE,
                                                   base_family = "Ubuntu"))
```
### Checking your COVID-19 data: the `skimr` package

#### We use the [`skimr`](https://docs.ropensci.org/skimr/) package to get a quick high-level view of some summary statistics across the entire dataset. `skimr` is especially helpful are the tiny histograms for continuous variables and the `complete_rate`

The `skimr` [package documentation](https://docs.ropensci.org/skimr/):

I like it because:

- It handles grouped data 

- It's output is plain text, so prints to console  

- It can be modified to add/remove summary statistics    

- `skimr` works in `knitr`/`rmarkdown` documents and `shiny` apps  

- `skimr` also has an abbreviated output when combined with `summary()` function 

***

### Examine responses with [`inspectdf::inspect_cat()`](https://alastairrushworth.github.io/inspectdf/) 

#### Check responses to categorical variables with `inspectdf::inspect_cat()` 

`covus` has a `data_quality_grade` variable that tells us a little about what to expect from each measurement. We can add `inspectdf::show_plot(text_labels = TRUE)` to see what the responses are.

```{r inspect_cat}
inspectdf::inspect_cat(df1 = select(covus, data_quality_grade)) %>% 
      inspectdf::show_plot(text_labels = TRUE, 
                       col_palette = 3)
```


- Check the [`covdata` package website](https://kjhealy.github.io/covdata/articles/covdata.html#exploring-the-data-1) for vignettes to explore the various data sources  

***


### covdata: compare datasets with [`inspectdf::inspect_na()`](https://alastairrushworth.github.io/inspectdf/) 

#### Compare the missing values in two datasets with `inspectdf::inspect_na()`

`covdata` contains two NYT datasets, the `nytcovcounty` and `nytcovstate` datasets,   

1. **`nytcovcounty`** = `NYT COVID-19 data for US counties, current as of Friday, July 17, 2020`    
2. **`nytcovstate`** = `NYT COVID-19 data for the US states, current as of Friday, July 17, 2020`

```{r inspect_types, echo=TRUE}
inspectdf::inspect_na(df1 = nytcovcounty,  
                      df2 = nytcovstate) %>% 
    inspectdf::show_plot(text_labels = TRUE, 
                       col_palette = 4)
```

***




### Check for missing data with [`visdat::vis_miss()`](https://visdat.njtierney.com/)

#### The `visdat::vis_miss()` visualization shows us where the missing data are in the `covid19us` dataset

Some of the data in these packages are missing, so I always make sure to check for missing patterns before doing any modeling. The description for the `covid19us` data tells us its *Open Source data from COVID Tracking Project on the distribution of Covid-19 cases and deaths in the US. For more, see https://github.com/opencovid19-fr/data* 

The `warn_large_data = FALSE` is necessary because of the number of observations.

```{r vis_miss-covid19us, warning=FALSE, message=FALSE}
visdat::vis_miss(covid19us, warn_large_data = FALSE) 
```

- Check out the entire [`visdat` vignette here](https://cran.r-project.org/web/packages/visdat/vignettes/using_visdat.html) for more info on how to use it

- Read the extensive `covid19R` documentation [here](https://covid19r.github.io/documentation/), written in `bookdown`

